### 2021-07-19 doc/thesis/chapters/system-design-process.tex
launch

>>>>

The system launch actually runs the system in a defined environment, so that it can perform what it is intended and designed to do.
The defined environment can be the final, operational environment, or just a simulation which provides an output that is detailed enough for an evaluation.
In a product that involves hardware development, this step may include the installation of commercial-off-the-shelf products with a modified prototype software.
However, since the SIMILAR process is applicable for any kind of problem, this might also be a business process, where the launch step may be the roll-out of the subprocesses and tasks in the respective departments of a company.
